MSHS COVID-19 Vaccination Summary

### 2022-09-14 MSH Vaccines Administered Hybrid Data Model.Rmd
Change tab name from Reference to Data Sources & Reference
Update code for 2022 vaccine administration summary to include additional departments and logic for Moderna <6yo vaccine.

# Import vaccine administration repository daily summary for Jan-Jun 2022
vax_admin_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-12.RDS"))

@@

    subset_data <- subset_data %>%
      group_by(Site, Dose) %>%
      summarize(Count = n()) %>%
      pivot_wider(names_from = Dose,
                  # names_prefix = "Dose ",
                  values_from = Count) %>%
      arrange(Site) %>%
      mutate(Total = sum(across(contains("Dose")), na.rm = TRUE),
             across(.cols = where(is.numeric),
                    .fns = ~replace_na(.x, 0))) %>%
      adorn_totals(where = "row",
                   name = "MSHS Total",
                   na.rm = TRUE)

@@

### Reference

@@

*   Immunizations with no associated Department/Epic ID excluded from analysis.
*   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
*   Vaccine dose based on Procedure Name field in Epic. Immunizations with ambiguous visit types are categorized as Dose 3/Booster.

>>>>

# Import vaccine administration repository daily summary for Jan-Jun 2022
vax_admin_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-19.RDS"))

@@

    subset_data <- subset_data %>%
      group_by(Site, Dose) %>%
      summarize(Count = sum(Count, na.rm = TRUE)) %>%
      pivot_wider(names_from = Dose,
                  # names_prefix = "Dose ",
                  values_from = Count) %>%
      arrange(Site) %>%
      mutate(Total = sum(across(contains("Dose")), na.rm = TRUE),
             across(.cols = where(is.numeric),
                    .fns = ~replace_na(.x, 0))) %>%
      adorn_totals(where = "row",
                   name = "MSHS Total",
                   na.rm = TRUE)

@@

### Data Sources & Reference

@@

*   Immunizations with no associated Department/Epic ID excluded from analysis.
*   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
*   Vaccine dose based on the following logic:
    1. PRC_NAME field in Epic for clearly defined visits.
    2. RESPONSE_LIST field completed during vaccination noting the dose in the series for ambiguously defined visits (ie, well visits, follow ups, etc.)
